Verifying Demonstrations

### 2017-08-04 design.tex
Renames primitives section to design
Edits design section, merges architecture

\section{Primitives}
\label{Primitives}

@@

\subsection{Authenticity}

@@

\begin{frame}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
  \begin{question}
    Can linear blockchains also fit in the framework of 
    \textcite{BlockchainFreeCryptocurrencies}?
    Can we generalize it?
  \end{question}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the \ac{tposet}.
      \item The proof must've been created before it was included (duh!).
      \item (Also related to V\ref{EligibilityVerif}.)
    \end{itemize}
  \end{solution}
\end{frame}

@@

\subsection{Location proofs}

@@

\subsection{Storage}

@@

\subsection{Verifiability}

>>>>

\section{Design}
\label{Design}

@@

\subsection{Eligibility verifiability}

We have the five requirements for eligibility verifiability.

\subsubsection{Temporal eligibility}

@@

\begin{frame}
  \begin{question}
    What about distributed voting/polling protocols?
    They must be complemented by time-stamping.
  \end{question}
  \begin{question}
    Can linear blockchains also fit in the framework of 
    \textcite{BlockchainFreeCryptocurrencies}?
    Can we generalize it?
  \end{question}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{solution}[V\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the \ac{tposet}.
      \item The proof must've been created before it was included (duh!).
    \end{itemize}
  \end{solution}
\end{frame}

@@

\subsubsection{Spatial eligibility}

@@

\subsubsection{Count only once}

We also need to ensure that proofs made by the same person must be linkable 
(\cref{UniqueIndividual}).

\subsubsection{Designated event}

We must ensure that the data is designated to the event 
(\cref{DesignatedEvent}), otherwise a counter-protest can copy the proofs and 
reuse them.

\begin{frame}
  \begin{question}
    How to designate a proof to an event?
    Include an event specific value?
  \end{question}
  \begin{question}
    How must this value be chosen?
    By the organizer?
    Randomly?
    Deterministically but unpredictably?
  \end{question}
\end{frame}

\subsection{Privacy}

\subsubsection{Architecture}

\begin{frame}
  \begin{question}
    Shall we offer a platform that is run by a variety of institutions who 
    offers to verify protests?
    Or go strictly peer-to-peer?
  \end{question}
  \begin{question}
    If strictly peer-to-peer, and only run by protesters, one can infer that 
    they are protesters by running such a node.
    Can this be mitigated?
  \end{question}
\end{frame}

\subsubsection{Storage}

@@

\subsubsection{Sybil}
